CdGF_aucrf

### 2016-10-05 code/CdGF_AUCRF.Rmd
add rel abund partial dependence overlay plots

#Importance Plot
n_rf_features <- 5
euth_otus <- euth_otu_feat[1:n_rf_features]
euth_tax <- get_tax(1, euth_otus, tax_file)
euth_tax$tax_label <- paste(euth_tax$tax, ' (', 
                            gsub('tu0*', 'TU ', rownames(euth_tax)), 
                                   ') : ', round(rf_early_aucrf$ranking[euth_otus], 3), sep = '')

@@

```{r partial dependence, fig.width=10, fig.height=5}
layout(matrix(c(1:6), nrow=2, byrow=TRUE))

for (i in seq_along(euth_otus)) {
  partialPlot(rf_early_aucrf$RFopt, aucrf_data, euth_otus[i], xlab='',
                main=paste(euth_tax$tax_label[i]))
}

>>>>

#Importance Plot
n_rf_features <- 9
euth_otus <- euth_otu_feat[1:n_rf_features]
euth_tax <- get_tax(1, euth_otus, tax_file)
euth_tax$tax_label <- paste(euth_tax$tax, ' (', 
                            gsub('tu0*', 'TU ', rownames(euth_tax)), 
                                   ') : ', round(rf_early_aucrf$ranking[euth_otus], 3), sep = '')

@@

```{r partial dependence, fig.width=10, fig.height=10}
layout(matrix(c(1:9), nrow=3, byrow=TRUE))

partial_otu <- c()
for (i in seq_along(euth_otu_feat)) {
  partial_otu <- partialPlot(rf_early_aucrf$RFopt, aucrf_data, euth_otu_feat[i], xlab='',
                main=paste(euth_tax$tax_label[i]))
points(Predict_early_euth_df[Predict_early_euth_df$Euth_Early == 0 ,euth_otu_feat[i]], 
       jitter(rep(0.75*(diff(range(partial_otu$y))) + min(partial_otu$y), 
                  sum(Predict_early_euth_df$Euth_Early == 0)), 
              amount = (0.1*(diff(range(partial_otu$y))))), 
              pch = 21, bg = 'red')
points(Predict_early_euth_df[Predict_early_euth_df$Euth_Early == 1 ,euth_otu_feat[i]], 
       jitter(rep(0.25*(diff(range(partial_otu$y))) + min(partial_otu$y), 
                  sum(Predict_early_euth_df$Euth_Early == 1)), 
              amount = (0.1*(diff(range(partial_otu$y))))), 
              pch = 21, bg = 'gray')
}
